Characterizing Stellar Streams by ML

### 2023-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

            % The specific architecture of the photometric normalizing flow are discussed in \autoref{sub:model_implementation}. But
            It is easy to evaluate the log-likelihood a normalizing flow at a point $\mbs{m}$ when all feature dimensions are present. When one (or more) feature dimension is missing, however, evaluating the marginal log-likelihood involves integrals over the flow. While the procedure is straightforward it is computationally expensive. As an alternative, we conservatively set the log-likelihood to $0$, the maximum value, overemphasizing the flow's contribution to the background model. Conceptually, up-weighting the background model decreases the false-positive rate in stream membership identification, at the
            cost of increasing the false-negative rate. However, the intrinsic width of stellar streams tends to be quite small, with correspondingly small $\sigma_\mu$ (see \autoref{eq:photometric_probability}); thus the effective region of the isochrone model is well determined and we do not find the marginal log-likelihood approach to be impactful. Another approach, which we leave to a future work, is to construct normalizing flows of each marginal distribution, e.g. $q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the features.

@@

>>>>

            % The specific architecture of the photometric normalizing flow are discussed in \autoref{sub:model_implementation}. But
            It is easy to evaluate the log-likelihood a normalizing flow at a point $\mbs{m}$ when all feature dimensions are present. When one (or more) feature dimension is missing, however, evaluating the marginal log-likelihood involves integrals over the flow. While the procedure is straightforward it is computationally expensive. As an alternative, we conservatively set the log-likelihood to $0$, the maximum value, overemphasizing the flow's contribution to the background model. Conceptually, up-weighting the background model decreases the false-positive rate in stream membership identification, at the
            cost of increasing the false-negative rate. However, the intrinsic width of stellar streams tends to be quite small, with correspondingly small $\sigma_\mu$ (see \autoref{eq:photometric_probability}); thus the effective region of the isochrone model is well determined and we do not find the marginal log-likelihood approach to be impactful. Another approach, which we leave to a future work, is to construct normalizing flows of each marginal distribution, e.g. $q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the present features.

@@

            We implement hard bounds on the range of each parameter $\theta$.
